---
title: "Extract Results"
output: html_notebook
---

# About this notebook

Written by AX (04/01/2019) <br><br>
**Purpose**<br>
1. Concatenate cluster text statistics into one .csv file<br>
2. Extract only the coordinates as a text file in order to input into Anatomy Toolbox on MATLAB<br>
<br>
**Input**: text files of cluster statistics<br>
--NOTE: This is equivalent to just putting the .Rproj into `clusterTexts`<br><br>
**Outputs**: <br>
1. `.csv` file of all contrast clusters concatenated into one<br>
2. `.txt` file of all coordinates
<br><br>
**NOTE**: Must keep directory structure exactly the same for best use.

# 1. Setup

Get the relevant functions needed for this notebook.<br>
<ul>
<li> `statsTable()` is a wrapper function that will output a dataframe of all the columns in the text files (with a variable `title` to indicate the text file the statistics came from). It depends on the function `readStatistics()` to do so (see documentation in script `setup.R`).</li>
</ul>

```{r}
source("setup.R")
```

# 2. Read in Data

<ol type="1">
<li>Set the working directory to the appropriate one given the analysis of interest. </li>
<li>Run `statsTable()` to output a dataframe of all the text files of interest in that directory.
</ol>

### A. Between-study Contrasts

```{r}
setwd("thresh")
contrastTables <- statsTable()
setwd("..")
```

### B. Main Effects

```{r}
setwd("mainEffects")
mainTables <- statsTable()
setwd("..")
```

### C. Conjunction

```{r}
setwd("conjunctions")
conjunctionTables <- statsTable()
setwd("..")
```

# 3. Bind everything and output

### A. Bind all and get only peak coordinates
```{r}
allData <- rbind(contrastTables, mainTables, conjunctionTables)
allData <- na.omit(allData)
coords <- allData[,4:6]
allData
coords
```

### B. Output relevant files
<ol type="A">
<li>`.csv` file of the results</li>
<li>`.txt` file of the coordinates</li>
</ol>
```{r}
write.csv(allData, "painHealthyResults_20190401.csv")
write.table(coords, "painHealthyResultsCoords_20190401.txt", sep=" ", row.names=F, col.names=F)
```